---
title: "Assesment"
author: "Shrinath"
date: "June 7, 2018"
output: html_document
Time started : 10:12 AM
---

# Problem Statement: Prediction the hospital readmissions for diabetes patients.


```{r}
train <- read.csv("C:/Users/patel/Desktop/data-challenge/training_data.csv")

```


# Exploring the data
```{r}
head(train)
str(train)
```

# Replacing all "?" with "NA"
 

```{r}
train[train=="?"]<-NA

```


# Since Columns "Weight", "Payer_code", and "medical_specialty" has larger NA values and it not significant much so removing those columns.

```{r}
train <-  train[ ,-c(6,11,12)] 

```

SInce i didn't know the output to to test my model i splitted my train data into training _set and test_set and trained my model on training_set dataset tested it on test_set dataset.
The output is categorical so its a classification problem so i can used Naive bayes, Logistic gression, Random forest and other classication algorithm.

```{r}
 #install.packages('caTools')
 library(caTools)
 set.seed(123)
 split = sample.split(train$readmitted, SplitRatio = 0.75)
 training_set = subset(train, split == TRUE)
 test_set = subset(train, split == FALSE)
 
 #install.packages('e1071')
 library(e1071)
 classifier = naiveBayes(x = training_set[-c(1,2,47)],
                         y = training_set$readmitted)
 
 # Predicting the Test set results
 y_pred = predict(classifier, newdata = test_set[-c(1,2,47)])
 
 # Making the Confusion Matrix
 cm = table(test_set[,47], y_pred)
cm 

```
# got 88.8 % accuracy

# build a model for original test data using naive bayes





